### 2022-01-08 paper/issta22/intro.tex
intro

Software testing is the cruicial process when developing software.  It
evaluates an attribute or capability of the software and determines
that it meets the requirements by examining the behavior of the
software under test. Software testing in the early stage of the
development finds bugs, and fixing them saves amount of costs. In
addition, reliable software testing methodology ensures software
quality to users in that the software meets requirements by
verification and validation. Regarding that, testing NLP application
becomes important process as well in that NLP application is a branch
of artifical intelligence software.

Prevalent NLP model is evaluated via train-validation-test
splits. train and validation set is used to train the NLP model and
the \ho set is used for testing by measuring accuracy

testing \ml becomes major

\Nlp testing is crucial part for developing a reliable \Nlp
applications. For developing \Nlp applications, testing is mainly used
to check the ML model's performance on \ho set with respect to the
accuracy of the model. The \ho data refers to a portion of dataset
that is held out of the datasets used for training \ml
models. Generally, the \ho set is extracted via Train-Validation-Test
split.

>>>>

Software testing is the cruicial process when developing software.  It
evaluates an attribute or capability of the software and determines
that it meets the requirements by examining the behavior of the
software under test. Software testing in the early stage of the
development finds bugs, and fixing them saves amount of costs. In
addition, reliable software testing methodology ensures software
quality to users in that the software meets requirements by
verification and validation. Regarding that, NLP application is a branch
of artifical intelligence software, and testing NLP application
also becomes important process as well.

The prevalent models of NLP are evaluated via train-validation-test
splits. train and validation set is used to train the NLP model and
the \ho set is used for testing by measuring accuracy. The accuracy is
a indicator of the performance of the models.

Despite its usefulness, the main limitation of the testing paradaigm
is that the \ho set often overestimates the performances. Each dataset
comes with specific biases, and the biases increase the discrepancy of
distribution between dataset and
real-world~\cite{recht2019imagenetbias}. The aforementioned accuracy
on \ho set does not consider the discrepancy and it is limited to
achieve comprehensive performrance of the NLP model. As a consequence,
it is difficult to analyze where the errors comes
from~\cite{wu2019errudite}.

On the subject of the limitation of traditional testing paradaigm, a
number of methods have been proposed. They approach evaluating
robustness of the model on adversarial sets~\cite{}, fairness~\cite{},
logical consistancy~\cite{}, explanations~\cite{}, diagnostic
datasets~\cite{}, and interactive error analysis. In addition,
inspired by the behavioral testing of software engineering research,
Marco \etal proposed a tool for comprehensive behavioral
testing of NLP models~\cite{marcoACL2020checklist}

%% Machine learning testing poses challenges that arise
%% from the fundamentally different nature and construction
%% of machine learning systems, compared to traditional (relatively more deterministic and less statistically-orientated)
%% software systems.

%% \Nlp testing is crucial part for developing a reliable \Nlp
%% applications. For developing \Nlp applications, testing is mainly used
%% to check the ML model's performance on \ho set with respect to the
%% accuracy of the model. The \ho data refers to a portion of dataset
%% that is held out of the datasets used for training \ml
%% models. Generally, the \ho set is extracted via Train-Validation-Test
%% split.
